gij bent 2

### 2025-09-28 paper/paper.qmd
I had broken the legend colours

@@

# Define cutoffs for adopter categories
mean_time <- 10
sd_time <- 2.5
cuts <- data.frame(
  x = c(mean_time - 2*sd_time, mean_time - sd_time, mean_time,
        mean_time + sd_time, mean_time + 2*sd_time),
  label = c("Innovators", "Early Adopters", "Early Majority", 
            "Late Majority", "Laggards"),
  col = c("red", "orange", "green3", "darkgreen", "blue")
)

# Plot
ggplot(df, aes(x = time)) +
  geom_line(aes(y = s_curve, colour = "S-curve (Cumulative Adoption)"), linewidth = 1) +
  geom_line(aes(y = bell_curve, colour = "Bell Curve (Adoption Rate)"), linewidth = 1, linetype = "dashed") +
  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
  scale_colour_manual(
    name = "Legend",
    values = c("S-curve (cumulative adoption)" = "purple",
               "Bell curve (adoption Rate)" = "deeppink",
               "Innovators" = "red",
               "Early adopters" = "orange",
               "Early majority" = "goldenrod3",
               "Late majority" = "darkgreen",
               "Laggards" = "blue")
  ) +
  labs(
    title = "S-curve and bell curve",
    x = "Time step",
    y = "Adoption percentage"
  ) +
  theme_minimal(base_size = 14)

>>>>

# TODO volgorde legende is fucked

@@

# Define cutoffs for adopter categories
mean_time <- 10
sd_time <- 2.5
cuts <- data.frame(
  x = c(mean_time - 2*sd_time, mean_time - sd_time, mean_time,
        mean_time + sd_time, mean_time + 2*sd_time),
  label = c("Innovators", "Early adopters", "Early majority", 
            "Late majority", "Laggards"),
  col = c("red", "orange", "green3", "darkgreen", "blue")
)

# Plot
ggplot(df, aes(x = time)) +
  geom_line(aes(y = s_curve, colour = "S-curve (cumulative adoption)"), linewidth = 1) +
  geom_line(aes(y = bell_curve, colour = "Bell Curve (adoption rate)"), linewidth = 1, linetype = "dashed") +
  geom_vline(data = cuts, aes(xintercept = x, colour = label), linetype = "dashed") +
  scale_colour_manual(
    name = "Legend",
    values = c("S-curve (cumulative adoption)" = "purple",
               "Bell curve (adoption Rate)" = "deeppink",
               "Innovators" = "red",
               "Early adopters" = "orange",
               "Early majority" = "goldenrod3",
               "Late majority" = "darkgreen",
               "Laggards" = "blue")
  ) +
  labs(
    title = "S-curve and bell curve",
    x = "Time step",
    y = "Adoption percentage"
  ) +
  theme_minimal(base_size = 14)
